|

### 2020-03-14 paper/paper.Rmd
printed second verison!

title: |
    New and old ways to chase a rabbit:  
    Differential item functioning detection methods
subtitle: |
    Ben Stenhaug  
    Stanford University
abstract: |
  summarize propose extensions insist as dif as student property and on communicating uncertainty
  <!-- https://tinyurl.com/ybremelq -->
header-includes: 
- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient
- \DeclareMathOperator*{\argmin}{arg\,min} # for gini coefficient

@@

# DIF methods

@@

# Next steps

```{r child = "paper_3_next_steps.Rmd"}
```

@@

# Notes

- adjust to all be easiness including multidimensional talk

# References

>>>>

title: |
    Promise and peril: Agnostic identification methods  
    for detecting differential item functioning
subtitle: |
    Ben Stenhaug, Ben Domingue, and Mike Frank  
    Stanford University
abstract: |
  It is well known that likelihood ratio tests (LRT) are effective at detecting differential item functioning (DIF) in item response models. However, to use an LRT, the model needs to be identified so that differences in group ability can be disentangled from potential DIF. We summarize existing assumptionless identification (AI) methods and propose a variety of new methods. We conduct a simulation study — which we believe to be more realistic than most DIF simulation studies in the literature — and find that one of the proposed new AI methods, All-others-as-anchors-one-at-a-time (AOAA-OAT), significantly outperforms current methods. We also offer a new method, the equal means, multiple imputation logit graph (EM-MILG), that presents clearly all information about possible DIF, including sampling variability in item parameters, to the analyst. \clearpage <!-- https://tinyurl.com/ybremelq -->
header-includes: 
- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient
- \DeclareMathOperator*{\argmin}{arg\,min} # for gini coefficient

@@

# Assumptionless identification methods

@@

# Simulation study

```{r child = "paper_3_sim.Rmd"}
```

@@
